### 2021-04-17 README.rmd
Generated the readme.md from readme.rmd

* FCM: Fuzzy C-Means, with the function `CMeans`
* GFCM: Generalized Fuzzy C-Means, with the function `GCMeans`
* SFCM: Spatial Fuzzy C-Means, with the function `SCMeans`
* SGFCM: Spatial Generalized Fuzzy C-Means, with the function `SGCMeans`

>>>>

* FCM: Fuzzy C-Means, with the function `CMeans`
* GFCM: Generalized Fuzzy C-Means, with the function `GFCMeans`
* SFCM: Spatial Fuzzy C-Means, with the function `SFCMeans`
* SGFCM: Spatial Generalized Fuzzy C-Means, with the function `SGFCMeans`
